\documentclass[10pt, letterpaper, twoside]{article}
\usepackage[utf8]{inputenc}
\usepackage{dirtytalk}
\usepackage[paperheight=16cm,
    paperwidth=12cm,
    top=15mm,
    bottom=20mm,
    left=2cm,
    right=2cm]{geometry}
\title{\textbf{Reformed ruling for ball games in the common room}}

\date{May 2022}

\begin{document}

\maketitle


\section*{\textbf{Introduction}}
\footnotesize The issue of ball games has become prevalent after damages incurred during a game. The currently ruling states: 

\say{Balls, frisbees or any other projectiles should not be thrown around in the space and must be kept in the cubbies at all time}

This rule is unfair to all who want to safely participate in ball games, and counterproductive for the development of adolescent mental health. Therefore I believe the rules should change to accurately hold students to account for any damages to the school while also allowing for safe play in the common room.

\section*{\textbf{Proposal}}
\footnotesize Damages to property or damage to others welling while playing ball games in the common room will results in a fine. The fine will included full reparations for damages encored. 10 \% of reparation costs will be added to the final bill and donated to the SSC (Senior Student Committee), as punishment. All claims of damage can be submitted via email to the SSC or on this website. <INSERT WEBSITE LINK>. Disputes to claims will be processed by the SSC. In these disputes the SSC will pick a plaintiff to represent the community while the defendant can chose to represent themselves. Their cases will be made to an independent jury of 5 randomly selected students. If consensus is not achieved, the student can appeal to school staff. All students who wish to participate in ball games must sign a waiver and create a video stating:

\say{I \textit{your name} will uphold the agreement stated in the reformed ruling of ball games.}

Any student who participates in ball games without agreeing to the stated terms will face a \$10 fine. If a student who does not agree to the terms damages either person or property while playing, the SSC and any responsible student will report them to faculty for disciplinary action.    

\end{document}